### 2018-04-04 defectLocalization/paper/paper_body.tex
-add text

Differently from previous work, the granularity of our experiment is on component level instead of on file level. 
Because we don't use the source code information to simulate a situation of strict source code security, new added files cannot be captured in the prediction with either VSM or DNN.
Thus we first truncate the path of a given file by removing the file name to obtain the component containing the given file. 
We assume that by knowing the potential defected component is enough for assigning the appropriate developer to solve the issue.
Because if a developer knows a component very well, he should also has knowledge to the new added file to that component.
After the truncation, there are\todo{add number} , , , , components in ZXing , SWT, Eclipse and AspectJ respectively. 
We didn't perform our experiment on the project AspectJ, since there are only two components in this data set, the result was highly inflated . 
The detail of the three data sets is summarized in table \todo{make the data set table}

>>>>

Differently from previous work, the granularity of our experiment is on component level instead of on file level. 
Because we don't use the source code information to simulate a situation of strict source code security, new added files cannot be captured in the prediction with either VSM or DNN.
Thus we first truncate the path of a given file by removing the file name to obtain the component containing the given file. 
We assume that by knowing the potential defected component is enough for assigning the appropriate developer to solve the issue.
Because if a developer knows a component very well, he should also has knowledge to the new added file to that component.
After the truncation, there are\todo{add number} , , , , components in ZXing , SWT, Eclipse and AspectJ respectively. 
For the project AspectJ, since there are only two components in this data set, the result was highly inflated.
Thus we perform the experiment on file level for the project AspecJ. 
The detail of the three data sets is summarized in table \todo{make the data set table}
